\section*{参考文献}
\begin{thebibliography}{99}

\bibitem{hunt2007letkf}
Hunt, B. R., Kostelich, E. J., \& Szunyogh, I. (2007).
Efficient data assimilation for spatiotemporal chaos: A local ensemble transform Kalman filter.
\textit{Physica D: Nonlinear Phenomena}, 230(1--2), 112--126.

\bibitem{kotsuki2024qda}
Kotsuki, S., Kawasaki, F., \& Ohashi, M. (2024).
Quantum data assimilation: a new approach to solving data assimilation on quantum annealers.
\textit{Nonlinear Processes in Geophysics}, 31, 237--245.

\bibitem{giannakis2022operator}
Giannakis, D., et al. (2022).
Data Assimilation in Operator Algebras.
\textit{arXiv preprint} arXiv:2206.13659.

\bibitem{calvello2025enkf}
Calvello, E., Reich, S., \& Stuart, A. M. (2025).
Ensemble Kalman methods: A mean field perspective.
\textit{Acta Numerica}, 34, 1--291.

\bibitem{felix2024reservoir}
Felix, O. A., Tennie, L., \& Magri, L. (2024).
Prediction of chaotic dynamics and extreme events: A recurrence-free quantum reservoir computing approach.
\textit{arXiv preprint} arXiv:2405.03390.

\bibitem{yin2025photonicqkernel}
Yin, Z., Agresti, I., de Felice, G., Brown, D., Toumi, A., Pentangelo, C., Piacentini, S., Crespi, A., Ceccarelli, F., Osellame, R., Coecke, B., \& Walther, P. (2025).
Experimental quantum-enhanced kernel-based machine learning on a photonic processor.
\textit{Nature Photonics}, 19, 1020--1027.

\bibitem{altmann2025qgk}
Altmann, P., Mansky, M. B., Zorn, M., Stein, J., \& Linnhoff-Popien, C. (2025).
Quantum Generator Kernels.
\textit{ICLR 2026 under review}. OpenReview: RbUe1cLXrJ.

\bibitem{saez2025qkernel}
S\'aez-Ortu\~no, L., Forgas-Coll, S., \& Ferrara, M. (2025).
Quantum Kernel Methods: Convergence Theory, Separation Bounds and Applications to Marketing Analytics.
\textit{arXiv preprint} arXiv:2510.11744.

\bibitem{sarp2025localization}
Er, S., \& Meldi, M. (2025).
Physics-based localization methodology for Data Assimilation by Ensemble Kalman Filter.
\textit{arXiv preprint} arXiv:2511.08845.

\bibitem{qtk2024}
Quantum tangent kernel. (2024).
\textit{Physical Review Research}, 6, 033179.

\bibitem{bansal2025qml}
Bansal, R., \& Rajput, N. K. (2025).
Quantum Machine Learning: Unveiling Trends, Impacts through Bibliometric Analysis.
\textit{arXiv preprint} arXiv:2504.07726.

\end{thebibliography}
